\vspace{-1cm}\Large{\textsf{The Size Distribution of Firms and Industrial Water Pollution: A Quantitative Analysis of China} \\ \textsf{Replication Instructions}}

### 2019-11-15 Documentation/Pollution_Final_AEJ_Template_Ver2.tex
final submission

\begin{table}[t]
\footnotesize
\centering
\caption{The Effects of Correlated Distortions and Environmental Regulations}
\begin{tabular}{lccccccc}
    \hline \hline
                         & \multicolumn{3}{c}{Polluting}    & & \multicolumn{3}{c}{Non-polluting} \\
    \cmidrule{2-4} \cmidrule{6-8}
    Statistics           & Benchmark & (i)      & (ii)      & & Benchmark     & (i)    & (ii) \\
    \hline
    Output               & 100.00    & 131.16   & 98.99     & & 100.00        & 129.62 & 100.28 \\
    Capital              & 100.00    & 163.06   & 99.00     & & 100.00        & 161.26 & 100.28 \\
    Consumption          & 100.00    & 123.63   & 100.02    & & 100.00        & 123.63 & 100.02 \\
    Wage                 & 100.00    & 160.00   & 99.96     & & 100.00        & 160.00 &  99.96 \\
    Output per Worker    & 100.00    & 128.25   & 100.15    & & 100.00        & 128.60 &  99.95 \\
    Output per Firm      & 100.00    & 297.62   & 110.17    & & 100.00        & 311.85 & 100.28 \\
    Average Productivity & 100.00    & 221.24   & 111.11    & & 100.00        & 235.39 & 100.00 \\
    \% in Output         & 19.73     & 19.91    & 19.52     & &  80.27        & 80.09  &  80.48 \\
    \hline
    \# of Firms          & 100.00    & 44.07    & 89.86     & & 100.00        & 41.56  & 100.00 \\
    Mean Size            & 59.98     & 139.19   & 65.98     & & 52.18         & 126.53 &  52.35 \\
    Median Size          & 23.67     & 43.09    & 27.88     & & 18.61         & 34.31  & 18.67  \\
    \hline
    Pollution            & 100       & 76.67    & 85.82     \\
    Intensity            & 100       & 58.46    & 86.73    \\
    Clean Share          & 57.77     & 85.61    & 85.10     \\
    Regulation           & 23.00     & 23.00    & 35.50     \\
    \hline
\end{tabular}
\begin{tablenotes}
     All values are percentages except for mean size and median size, which are the numbers of workers. Consumption and wage are not sector specific.
\end{tablenotes}
\label{tab:aggregates}
\end{table}

\begin{table}[t]
\footnotesize
\centering
\caption{Resource Allocation on the Intensive Margin}
\begin{tabular}{lccccc}
    \hline \hline
    Economy           & $\text{QU}_1$ & $\text{QU}_2$ & $\text{QU}_3$ & $\text{QU}_4$ & $\text{QU}_5$ \\
    \hline
    \multicolumn{3}{l}{\textbf{Polluting Sector:}} \\
    \ \ \ Benchmark   & 2.79          & 4.26          & 7.45          & 16.81         & 68.70          \\
    \ \ \ Case (i)    & 1.53          & 2.89          & 6.46          & 18.25         & 70.87          \\
    \ \ \ Case (ii)   & 3.02          & 4.63          & 8.01          & 17.79         & 66.55          \\
    \hline
    \multicolumn{3}{l}{\textbf{Non-polluting Sector:}} \\
    \ \ \ Benchmark   & 2.42          & 3.78          & 6.65          & 15.39         & 71.75          \\
    \ \ \ Case (i)    & 1.30          & 2.49          & 5.68          & 16.97         & 73.57          \\
    \ \ \ Case (ii)   & 2.42          & 3.78          & 6.65          & 15.39         & 71.75          \\
    \hline
\end{tabular}
\begin{tablenotes}
     $\text{QU}_1$ to $\text{QU}_5$ represent the first to fifth quintiles, respectively.
\end{tablenotes}
\label{tab:talentdist}
\end{table}

@@

\begin{table}[t]
\footnotesize
\centering
\caption{The Effects of the Progressivity of Distortions}
\begin{tabular}{lccccccc}
    \hline \hline
                         & \multicolumn{3}{c}{Polluting}    & & \multicolumn{3}{c}{Non-polluting} \\
    \cmidrule{2-4} \cmidrule{6-8}
    Statistics           & Benchmark & (i')      & (i)      & & Benchmark     & (i')    & (i) \\
    \hline
    Output               & 100.00    & 108.15   & 131.16    & & 100.00        & 106.87 & 129.62 \\
    Capital              & 100.00    & 110.91   & 163.06    & & 100.00        & 109.63 & 161.26 \\
    Consumption          & 100.00    & 106.57   & 123.63    & & 100.00        & 106.57 & 123.63 \\
    Wage                 & 100.00    & 108.76   & 160.00    & & 100.00        & 108.76 & 160.00 \\
    Output per Worker    & 100.00    & 105.74   & 128.25    & & 100.00        & 106.03 & 128.60 \\
    \hline
    \# of Firms          & 100.00    & 44.07    &44.07      & & 100.00        & 41.56  & 41.56 \\
    Mean Size            & 59.98     & 139.19   & 139.19    & & 52.18         & 126.53 & 126.53 \\
    \hline
    Pollution            & 100       & 70.04    & 76.67     \\
    Intensity            & 100       & 64.78    & 58.46     \\
    Clean Share          & 57.77     & 73.33    & 85.61     \\
    \hline
\end{tabular}
\begin{tablenotes}
     All of the values are percentages except for mean firm size, which are the numbers of workers. Consumption and wage are not sector specific.
\end{tablenotes}
\label{tab:uniform}
\end{table}

>>>>

\begin{table}[t]
\footnotesize
\centering
\caption{The Effects of Correlated Distortions and Environmental Regulations}
\begin{tabular}{lccccccc}
    \hline \hline
                         & \multicolumn{3}{c}{Polluting}    & & \multicolumn{3}{c}{Non-polluting} \\
    \cmidrule{2-4} \cmidrule{6-8}
    Statistics           & Benchmark & (i)      & (ii)      & & Benchmark     & (i)    & (ii) \\
    \hline
    Output               & 100.00    & 131.16   & 98.99     & & 100.00        & 129.62 & 100.28 \\
    Capital              & 100.00    & 163.06   & 99.00     & & 100.00        & 161.26 & 100.28 \\
    Consumption          & 100.00    & 123.63   & 100.02    & & 100.00        & 123.63 & 100.02 \\
    Wage                 & 100.00    & 160.00   & 99.95     & & 100.00        & 160.00 &  99.95 \\
    Output per Worker    & 100.00    & 128.25   & 100.15    & & 100.00        & 128.60 &  99.95 \\
    Output per Firm      & 100.00    & 297.62   & 110.17    & & 100.00        & 311.85 & 100.28 \\
    Average Productivity & 100.00    & 221.24   & 111.11    & & 100.00        & 235.39 & 100.00 \\
    \% in Output         & 19.73     & 19.91    & 19.52     & &  80.27        & 80.09  &  80.48 \\
    \hline
    \# of Firms          & 100.00    & 44.07    & 89.85     & & 100.00        & 41.56  & 100.00 \\
    Mean Size            & 59.98     & 139.19   & 65.98     & & 52.18         & 126.53 &  52.35 \\
    Median Size          & 23.67     & 43.09    & 27.88     & & 18.61         & 34.31  & 18.67  \\
    \hline
    Pollution            & 100       & 76.67    & 85.83    \\
    Intensity            & 100       & 58.45    & 86.70    \\
    Clean Share          & 57.77     & 85.61    & 85.10     \\
    Regulation           & 23.00     & 23.00    & 35.50     \\
    \hline
\end{tabular}
\begin{tablenotes}
     All values are percentages except for mean size and median size, which are the numbers of workers. Consumption and wage are not sector specific.
\end{tablenotes}
\label{tab:aggregates}
\end{table}

\begin{table}[t]
\footnotesize
\centering
\caption{Resource Allocation on the Intensive Margin}
\begin{tabular}{lccccc}
    \hline \hline
    Economy           & $\text{QU}_1$ & $\text{QU}_2$ & $\text{QU}_3$ & $\text{QU}_4$ & $\text{QU}_5$ \\
    \hline
    \multicolumn{3}{l}{\textbf{Polluting Sector:}} \\
    \ \ \ Benchmark   & 2.79          & 4.26          & 7.45          & 16.81         & 68.70          \\
    \ \ \ Case (i)    & 1.53          & 2.89          & 6.46          & 18.25         & 70.87          \\
    \ \ \ Case (ii)   & 3.02          & 4.63          & 8.01          & 17.79         & 66.55          \\
    \hline
    \multicolumn{3}{l}{\textbf{Non-polluting Sector:}} \\
    \ \ \ Benchmark   & 2.43          & 3.78          & 6.65          & 15.39         & 71.75          \\
    \ \ \ Case (i)    & 1.30          & 2.49          & 5.68          & 16.97         & 73.57          \\
    \ \ \ Case (ii)   & 2.43          & 3.78          & 6.65          & 15.39         & 71.75          \\
    \hline
\end{tabular}
\begin{tablenotes}
     $\text{QU}_1$ to $\text{QU}_5$ represent the first to fifth quintiles, respectively.
\end{tablenotes}
\label{tab:talentdist}
\end{table}

@@

\begin{table}[t]
\footnotesize
\centering
\caption{The Effects of the Progressivity of Distortions}
\begin{tabular}{lccccccc}
    \hline \hline
                         & \multicolumn{3}{c}{Polluting}    & & \multicolumn{3}{c}{Non-polluting} \\
    \cmidrule{2-4} \cmidrule{6-8}
    Statistics           & Benchmark & (i')      & (i)      & & Benchmark     & (i')    & (i) \\
    \hline
    Output               & 100.00    & 108.15   & 131.16    & & 100.00        & 106.87 & 129.62 \\
    Capital              & 100.00    & 110.91   & 163.06    & & 100.00        & 109.63 & 161.26 \\
    Consumption          & 100.00    & 106.57   & 123.63    & & 100.00        & 106.57 & 123.63 \\
    Wage                 & 100.00    & 108.77   & 160.00    & & 100.00        & 108.77 & 160.00 \\
    Output per Worker    & 100.00    & 105.74   & 128.25    & & 100.00        & 106.03 & 128.60 \\
    \hline
    \# of Firms          & 100.00    & 44.07    & 44.07     & & 100.00        & 41.56  & 41.56 \\
    Mean Size            & 59.98     & 139.19   & 139.19    & & 52.18         & 126.53 & 126.53 \\
    \hline
    Pollution            & 100       & 70.04    & 76.67     \\
    Intensity            & 100       & 64.77    & 58.45     \\
    Clean Share          & 57.77     & 73.34    & 85.61     \\
    \hline
\end{tabular}
\begin{tablenotes}
     All of the values are percentages except for mean firm size, which are the numbers of workers. Consumption and wage are not sector specific.
\end{tablenotes}
\label{tab:uniform}
\end{table}

### 2019-11-15 Documentation/Replication_Instruction.tex
slides
final submission

This note explains step-by-step how to replicate all the results in \textit{The Size Distribution of Firms and Industrial Water Pollution: A Quantitative Analysis of China}. We begin with some housekeeping stuff in Section \rom{1}. Section \rom{2} explains in detail how to replicate all the results in the main text. Section \rom{3} shows how the results in the appendices can be replicated.

@@

To replicate all the results in the paper, three softwares are used. Specifically, \textsc{Stata} is used for initial data processing. All the empirical results are then produced using \code{R}. MATLAB is used to compute all the quantitative results. There is no particular scientific reason that we use one statistical software (\textsc{Stata}) for data cleaning and the other (\code{R}) for empirical analysis.\footnote{Due to limited backward compatibility of \textsc{Stata} and that the \code{foreign} package of \code{R} supports only \code{.dta} files saved by \textsc{Stata} up to Version 12, to run the code without any modification, the reader would need \textsc{Stata} 12. Readers with more recent version of \textsc{Stata} would need to either modify in the \code{.do} file everywhere \code{.dta} files are read and written, or use alternative \code{R} package (for instance \code{readstata13}) to convert the data in \bcode{cpsc\_convert.R} and \bcode{cec\_convert.R}. Compatibility of our code is not tested under such environments. However, none of our results should be affected though.} Veterans of \textsc{Stata} or \code{R} should be able to replicate all the empirical results with just one software using our source code as reference with ease. In addition, it should go without saying that for readers without a licence to MATALB, GNU Octave could be used instead.

@@

    For an official introduction to the NGSPS and declassified information at the aggregated level, interested readers could refer to the book \textit{Data Collection of the National General Survey of Pollution Sources} (\begin{CJK}{GBK}{kai}《污染源普查数据集》, 中国环境科学出版社, 2011\end{CJK}), which is publicly available. We provide a summary in English in Online Appendix A of our paper.
    \item
    The CNEC is also a confidential dataset belonging to National Bureau of Statistics of China. Many universities and institutions have legal copy of the dataset though. Our copy was obtained from Fudan University.
    \item
    The SUSB is publicly available from the Census Bureau's dedicated website. The url, retrieved on September 15th, 2019, and subject to possible change in the future, is \url{https://www.census.gov/programs-surveys/susb.html}.
\end{itemize}

@@

The readers will get a number of files for replicating the results. To ease digestion, we briefly introduce the structure of the folders and files. As typographical convention, we use \bcode{blue computer modern typewriter} to indicate \bcode{folders} and \bcode{files}. The parent folder is referred to as \bcode{./}.
\begin{itemize}
    \item
    \bcode{./Empirical/}:
    \begin{itemize}
        \item
        \bcode{./Data/}: contains the raw and cleaned data.
        \item
        \bcode{./Results/}: contains all the figures and log-files.
        \item
        \bcode{./cpsc\_raw.do}: does initial processing of the NGSPS.
        \item
        \bcode{./cec\_clean.do}: does initial processing of the CNEC.
        \item
        \bcode{./cpsc\_convert.R}: converts the NGSPS to the binary format of \code{R}.
        \item
        \bcode{./cec\_convert.R}: converts the CNEC to the binary format of \code{R}.
        \item
        \bcode{./Empirical\_AEJ.R}: produces most empirical results in the main text.
        \item
        \bcode{./Empirical\_Appendix.R} produces most empirical results in the appendices.
        \item
        \bcode{./Accounting.R}: executes the accounting exercise.
        \item
        \bcode{./Descriptive.R}: computes some summary statistics of the NGSPS.
    \end{itemize}
    \item
    \bcode{./Quantitative/}
    \begin{itemize}
        \item
        \bcode{./Results/}: contains all the results and figures.
        \item
        \bcode{./twosectors.m}: computes the equilibrium of the two-sector model with perfect substitution used in the main text and saves the results in \bcode{.mat} format.
        \item
        \bcode{./fcn2.m}: computes the excess demand at a given vector of price; called by \bcode{twosectors.m}.
        \item
        \bcode{./compute\_tables.m}: computes the raw data used to calculate Tables 4, 5 and 6 in the main text.
        \item
        \bcode{./plot\_figures.m}: plots Figures 5 and 6 in the main text.
        \item
        \bcode{./twosectors\_ces.m}: computes the equilibrium of the two-sector model with constant elasticity of substitution used in Appendix J and saves the results in \bcode{.mat} format.
        \item
        \bcode{./fcnces.m}: computes the excess demand at a given vector of price; called by \\
        \bcode{twosectors\_ces.m}.
        \item
        \bcode{./compute\_tables\_ces.m}: computes the raw data used to calculate Tables J.1 in Appendix J.
        \item
        \bcode{./misc.m}: draws Figure D.2 and computes the decomposition in Sections \rom{4}.A and \rom{4}.B of the main text.
    \end{itemize}
\end{itemize}

@@

With these two steps completed, the reader needs to convert the data from \textsc{Stata} \code{.dta} format to the internal binary \code{R} format \code{.RData}. The file \bcode{cpsc\_convert.R} converts \bcode{keynum.dta} to \bcode{KEYFIRM\_R.RData}, \bcode{regall.dta} to \bcode{REGFIRM\_R.RData} and \bcode{allfirms.dta} to \bcode{ALLFIRM\_R.RData}. Similarly, \bcode{cec\_convert.R} converts \\ \bcode{cec2004\_small.dta} to \bcode{DSMALL\_R.RData}, \bcode{cec2004\_large\_full.dta} to \bcode{DLARGE\_R.RData}. It then extracts only the variables used in the paper and combines the two \code{.RData} files to one file \bcode{CNEC\_avgp.RData}. All the files are saved under \bcode{./Empirical/Data/} as before.

@@

In what follows, we will only use the files converted by \code{R}. A list of the essential files is provided below. All the files should be placed under \bcode{./Empirical/Data/}. For ease of reference, we use the two-letter acronyms in parenthesis when referring to the data files later.
\begin{itemize}
    \item
    \bcode{KEYFIRM\_R.RData (PK)}: Key sources of the NGSPS.
    \item
    \bcode{ALLFIRM\_R.RData (PA)}: All sources of the NGSPS.
    \item
    \bcode{CNEC\_avgp.RData (CA)}: All samples in the CNEC.
    \item
    \bcode{DLARGE\_R.RData (DL)}: A subset of \code{CA} which overlaps with the 2004 ASIF.
    \item
    \bcode{susb04.csv (US)}: SUSB 2004.
\end{itemize}

@@

    The in-text number of the accounting exercise can be calculated from the results when executing \bcode{Accounting.R}. The 33\% reduction in the last paragraph of Section \rom{1}.C part \textit{An Accounting Exercise} can then be calculated as the weighted average of the variable \bcode{ppar} with Row 1 of Table 1 being the weight. Notice that the variable \bcode{ppar} is exactly Row 3 of Table F.1. Because according to Row 1 of Table 1, the five industries combined contribute to 77\% of total COD emission, assuming that industries emitting the other 23\% COD remain intact, the 25\% reduction in average intensity is simply calculated as $1 - (67\% \times 77\% + 100\% \times 23\%) \triangleq 25\%$.

@@

    Tables 4, 5 and 6 are calculated using the output of \bcode{compute\_tables.m}. Notice that Tables 4 and 6 are presented in relative changes and share a similar structure. By changing the input files at the beginning of \bcode{compute\_tables.m} (in particular the 4 \code{.mat} just computed), \bcode{compute\_tables.m} prints the raw data of the corresponding entries in the same structure as the tables in the paper. Table 5 can be directly taken from the output \code{Table 5} after executing \bcode{compute\_tables.m} with the input being the corresponding cases. Entries in Table 4 can be calculated from the \code{Table 4} of the benchmark case and Cases (i) and (ii), while that of Table 6 can be calculated from \code{Table 4} of the benchmark case and Case (i'). The calculations of the relative changes are not automated, and the reader does have to do the calculations manually as we did. We apologize for the inconvenience.

    The in-text decomposition of total reduction to the contribution of size distribution and technology adoption can be performed using \bcode{misc.m}. The reader needs to change the second input file to either \bcode{notax\_new.mat} or \bcode{regulation\_new.mat}, depending on the case to compute. The role of technology adoption is printed to the terminal, with the residual being that from the size distribution.
    \item
    Several calibration targets are computed from the data as well. This last bulletin point explains where they are computed.
    \begin{itemize}
        \item
        The share of firms using clean technology 57\% is calculated in Section 2 of \bcode{Empirical\_AEJ.R}. The variable \code{clean\_share} hosts the number.
        \item
        The average adoption cost of clean technology as a ratio of output for clean firms 2.5\% is calculated at the end of Section 2 of \bcode{Empirical\_AEJ.R}. The number is printed to the terminal directly.
        \item
        The value of $\phi_1$ is computed in the first part of Section 4 of \bcode{Empirical\_AEJ.R}. The variable \code{phi\_quant} carries the information.
        \item
        The firm size and employment distributions [the light (yellow) bars in Figure 5] are computed at the end of Section 3 of \bcode{Empirical\_AEJ.R}. The variable \code{distchn} is first used to save the employment distribution and then the firm size distribution.
    \end{itemize}
\end{enumerate}

@@

    With all the \code{*.mat} files computed, as before, \bcode{compute\_tables\_ces.m} computes the raw data used in calculating entries in Table J.1. The results printed to the terminal can then be used to compute the percentage changes between equilibria in Table J.1. In particular, with the three cases at hand, the upper panel of Table J.1 can be reproduced.

@@

    Repeating Steps 9 and 10 with the parameters set to CES $=$ 3.0 then produces the lower panel of Table J.1, which finally completes the replication of all the results in our paper.

@@

Right before our final submission, we did a final test run on all the programs. We saved all the log files of this particular run in \code{.pdf} format. The correspondence between the log files and the source code is as follows. The original log files are saved in text files of \code{.log} extension with the same names. For instance, executing the source code \bcode{cpsc\_raw.do} will generate a text log file \bcode{cpsc\_raw.log}, which we converted to \bcode{cpsc\_raw\_log.pdf} manually.
\begin{itemize}
    \item
    \bcode{cpsc\_raw.do} $\longleftrightarrow$ \bcode{cpsc\_raw\_log.pdf}
    \item
    \bcode{cec\_clean.do} $\longleftrightarrow$ \bcode{cec\_clean\_log.pdf}
    \item
    \bcode{cpsc\_convert.R} $\longleftrightarrow$ \bcode{cpsc\_convert\_log.pdf}
    \item
    \bcode{cec\_convert.R} $\longleftrightarrow$ \bcode{cec\_convert\_log.pdf}
    \item
    \bcode{Empirical\_AEJ.R} $\longleftrightarrow$ \bcode{empirical\_main\_log.pdf}
    \item
    \bcode{Empirical\_Appendix.R} $\longleftrightarrow$ \bcode{empirical\_appendix\_log.pdf}
    \item
    \bcode{Descriptive.R} $\longleftrightarrow$ \bcode{descriptive\_log.pdf}
    \item
    \bcode{Accounting.R} $\longleftrightarrow$ \bcode{accounting\_log.pdf}
\end{itemize}
The log files for the quantitative exercises are not automatically generated. We manually copied and pasted the intermediate results sent to the terminal to two text files: \bcode{quantitative\_main.log} for the perfect substitute case in the main text and \bcode{quantitative\_ces.log} for the constant elasticity of substitution case in the appendix. Then we convert the two files to \code{.pdf} format.
\begin{itemize}
    \item
    \bcode{quantitative\_main\_log.pdf} $\longleftrightarrow$ \bcode{quantitative\_main.log}
    \item
    \bcode{quantitaitve\_ces\_log.pdf} $\longleftrightarrow$ \bcode{quantitative\_ces.log}
\end{itemize}

>>>>

This note explains step-by-step how to replicate all the results in \textit{The Size Distribution of Firms and Industrial Water Pollution: A Quantitative Analysis of China}. We begin with some housekeeping stuff in Section \rom{1}. Section \rom{2} explains in detail how to replicate all the results in the main text. Section \rom{3} shows how the results in the appendices can be replicated. The data and code can be downloaded from the AEA Data and Code Repository (OPENICPSR-112005).

@@

To replicate all the results in the paper, three softwares are used. Specifically, \textsc{Stata} is used for initial data processing. All the empirical results are then produced using \code{R}. MATLAB is used to compute all the quantitative results. There is no particular scientific reason that we use one statistical software (\textsc{Stata}) for data cleaning and the other (\code{R}) for empirical analysis. Veterans of \textsc{Stata} or \code{R} should be able to replicate all the empirical results with just one software using our source code as reference with ease. In addition, it should go without saying that for readers without a licence to MATALB, GNU Octave could be used instead.

The specific versions we use are: \textsc{Stata} 12, \texttt{R} 3.5.3 (code name \textit{Great Truth}) and MATLAB R2016a. The readers may need to do some very minor syntax change if using other versions. None of our results should be affected though. We did test our code in other versions of the softwares to the best as we could. Below are two examples:
\begin{itemize}
    \item
    Due to limited backward compatibility of \textsc{Stata} and that the \code{foreign} package of \code{R} supports only \code{.dta} files saved by \textsc{Stata} up to Version 12, readers with more recent version of \textsc{Stata} would need to either modify in the \code{.do} file everywhere \code{.dta} files are read and written, or use alternative \code{R} package (for instance \code{readstata13}) to convert the data in \bcode{cpsc\_convert.R} and \bcode{cec\_convert.R}.
    \item
    The syntax for several routines was slightly changed in MATLAB R2014b. If vintage versions are used, the reader would get a complaint saying (here from R2014a)
\begin{verbatim}    
Error using optimoptions (line 105)
'OptimalityTolerance' is not an option for FSOLVE.
A list of options can be found on the FSOLVE documentation page.
\end{verbatim}
    The code would run through by simply fixing the syntax to R2014a version; namely, the keywords to two optimization option need to be changed to \code{TolFun} and \code{MaxIter}. The code will run through seamlessly.
\end{itemize}

@@

    For an official introduction to the NGSPS and declassified information at the aggregated level, interested readers could refer to the book \textit{Data Collection of the National General Survey of Pollution Sources} (\begin{CJK}{GBK}{kai}《污染源普查数据集》, 中国环境科学出版社, 2011\end{CJK}), which is publicly available. We provide a summary in English in Online Appendix A of our paper.
    \item
    The CNEC is also a confidential dataset belonging to National Bureau of Statistics of China. Many universities and institutions have legal copy of the dataset though. Our copy was obtained from Fudan University. \\ \rtext{MORE INFORMATION IS NEEDED HERE!!!!!!!!}
    \item
    The SUSB is publicly available from the Census Bureau's dedicated website. The url, retrieved on September 15th, 2019, and subject to possible change in the future, is \url{https://www.census.gov/programs-surveys/susb.html}.
\end{itemize}

@@

The readers will get a number of files for replicating the results. To ease digestion, we briefly introduce the structure of the folders and files. As typographical convention, we use \bcode{blue computer modern typewriter} to indicate \bcode{folders} and \bcode{files}. The parent folder is referred to as \bcode{./}.
\begin{itemize}
    \item
    \bcode{./Empirical/}:
    \begin{itemize}
        \item
        \bcode{./Data/}: contains the raw and cleaned data.
        \item
        \bcode{./Results/}: contains all the figures and log-files.
        \item
        \bcode{./cpsc\_raw.do}: does initial processing of the NGSPS.
        \item
        \bcode{./cec\_clean.do}: does initial processing of the CNEC.
        \item
        \bcode{./cpsc\_convert.R}: converts the NGSPS to the binary format of \code{R}.
        \item
        \bcode{./cec\_convert.R}: converts the CNEC to the binary format of \code{R}.
        \item
        \bcode{./Empirical\_AEJ.R}: produces most empirical results in the main text.
        \item
        \bcode{./Empirical\_Appendix.R} produces most empirical results in the appendices.
        \item
        \bcode{./Accounting.R}: executes the accounting exercise.
        \item
        \bcode{./Descriptive.R}: computes some summary statistics of the NGSPS.
    \end{itemize}
    \item
    \bcode{./Quantitative/}
    \begin{itemize}
        \item
        \bcode{./Results/}: contains all the results and figures.
        \item
        \bcode{./twosectors.m}: computes the equilibrium of the two-sector model with perfect substitution used in the main text and saves the results in \bcode{.mat} format.
        \item
        \bcode{./fcn2.m}: computes the excess demand at a given vector of price; called by \bcode{twosectors.m}.
        \item
        \bcode{./generate\_tables\_main.m}: prints Tables 4, 5 and 6 in the main text.
        \item
        \bcode{./plot\_figures.m}: plots Figures 5 and 6 in the main text.
        \item
        \bcode{./twosectors\_ces.m}: computes the equilibrium of the two-sector model with constant elasticity of substitution used in Appendix J and saves the results in \bcode{.mat} format.
        \item
        \bcode{./fcnces.m}: computes the excess demand at a given vector of price; called by \\
        \bcode{twosectors\_ces.m}.
        \item
        \bcode{./generate\_tables\_appendix.m}: prints Table J.1 in Appendix J.
        \item
        \bcode{./misc.m}: draws Figure D.2 and computes the decomposition in Sections \rom{4}.A and \rom{4}.B of the main text.
    \end{itemize}
\end{itemize}

@@

With these two steps completed, the reader needs to convert the data from \textsc{Stata} \code{.dta} format to the internal binary \code{R} format \code{.RData}. The file \bcode{cpsc\_convert.R} converts \bcode{keynum.dta} to \bcode{KEYFIRM\_R.RData}, \bcode{regall.dta} to \bcode{REGFIRM\_R.RData} and \bcode{allfirms.dta} to \bcode{ALLFIRM\_R.RData}. Similarly, \bcode{cec\_convert.R} converts \bcode{cec2004\_small.dta} to \bcode{DSMALL\_R.RData}, \bcode{cec2004\_large\_full.dta} to \bcode{DLARGE\_R.RData}. It then extracts only the variables used in the paper and combines the two \code{.RData} files to one file \\ \bcode{CNEC\_avgp.RData}. All the files are saved under \bcode{./Empirical/Data/} as before.

@@

In what follows, we will only use the files converted by \code{R}. A list of the essential files is provided below. All the files should be placed under \bcode{./Empirical/Data/}. For ease of reference, we use the two-letter acronyms in parenthesis when referring to the data files later.
\begin{itemize}
    \item
    \bcode{KEYFIRM\_R.RData (PK)}: Key sources of the NGSPS.
    \item
    \bcode{ALLFIRM\_R.RData (PA)}: All sources of the NGSPS.
    \item
    \bcode{CNEC\_avgp.RData (CA)}: All samples in the CNEC.
    \item
    \bcode{DLARGE\_R.RData (DL)}: A subset of \code{CA} which overlaps with the 2004 ASIF.
    \item
    \bcode{susb04.csv (US)}: SUSB 2004.
\end{itemize}
Because we cannot post the NGSPS and CNEC publicly, the readers will not be able to run some of the files. Tables \ref{tab:navi_main} and \ref{tab:navi_appendix} list respectively which part of each file depends on which datasets and generates which results; the datasets are referenced using the above two-letter acronyms.

@@

    The in-text number of the accounting exercise can be calculated from the results when executing \bcode{Accounting.R}. The 33\% reduction in the last paragraph of Section \rom{1}.C part \textit{An Accounting Exercise} can then be calculated as the weighted average of the variable \bcode{ppar} with Row 1 of Table 1 being the weight. Notice that the variable \bcode{ppar} is exactly Row 3 of Table F.1. Because according to Row 1 of Table 1, the five industries combined contribute to 77\% of total COD emission, assuming that industries emitting the other 23\% COD remain intact, the 25\% reduction in average intensity is simply calculated as $1 - (67\% \times 77\% + 100\% \times 23\%) \triangleq 25\%$. The calculation of the two numbers are automated in the code.

@@

    Similarly, file \bcode{generate\_tables\_main.m} reads the four \code{.mat} files and prints Tables 4, 5 and 6 to MATLAB terminal.
    %Tables 4, 5 and 6 are calculated using the output of \bcode{compute\_tables.m}. Notice that Tables 4 and 6 are presented in relative changes and share a similar structure. By changing the input files at the beginning of \bcode{compute\_tables.m} (in particular the 4 \code{.mat} just computed), \bcode{compute\_tables.m} prints the raw data of the corresponding entries in the same structure as the tables in the paper. Table 5 can be directly taken from the output \code{Table 5} after executing \bcode{compute\_tables.m} with the input being the corresponding cases. Entries in Table 4 can be calculated from the \code{Table 4} of the benchmark case and Cases (i) and (ii), while that of Table 6 can be calculated from \code{Table 4} of the benchmark case and Case (i'). The calculations of the relative changes are not automated, and the reader does have to do the calculations manually as we did. We apologize for the inconvenience.

    The in-text decomposition of total reduction to the contribution of size distribution and technology adoption can be performed using \bcode{misc.m}.\footnote{The code snippet \textit{must be} executed by using the MATLAB shortcut of 'Select $\rightarrow$ F9'. Executing \bcode{misc.m} by using the \textit{Run} command in MATLAB toolstrip would yield an error when calling the function \code{plot}. This is confirmed to be a known issue by staff from MathWorks. The supporting team claims that the issue has been fixed in MATLAB R2019b. We were not able to test the code under the environment.} The reader needs to change the second input file to either \bcode{notax\_new.mat} or \bcode{regulation\_new.mat}, depending on the case to compute. The role of technology adoption is printed to the terminal, with the residual being that from the size distribution.
    \item
    Several calibration targets are computed from the data as well. This last bulletin point explains where they are computed.
    \begin{itemize}
        \item
        The share of firms using clean technology 57\% is calculated in Section 2 of \bcode{Empirical\_AEJ.R}. The variable \code{clean\_share} hosts the number.
        \item
        The average adoption cost of clean technology as a ratio of output for clean firms 2.5\% is calculated at the end of Section 2 of \bcode{Empirical\_AEJ.R}. The number is printed to the terminal directly.
        \item
        The value of $\phi_1$ is computed in the first part of Section 4 of \bcode{Empirical\_AEJ.R}. The variable \code{phi\_quant} carries the information.
        \item
        The firm size and employment distributions [the light (yellow) bars in Figure 5] are computed at the end of Section 3 of \bcode{Empirical\_AEJ.R}. The variable \code{distchn} is first used to save the employment distribution and then the firm size distribution.
    \end{itemize}
\end{enumerate}

@@

    Repeat Step 9 with the parameters set to CES $=$ 3.0 will generate three corresponding \code{.mat} files:
    \begin{itemize}

@@

        \bcode{./Quantitative/Results/benchmark\_ces3.mat}
        \bcode{./Quantitative/Results/nodirty\_ces3.mat}
        \bcode{./Quantitative/Results/notax\_ces3.mat}
    \end{itemize}
    With all the \code{*.mat} files computed, as before, \bcode{generate\_tables\_appendix} prints Table J.1 to MATLAB terminal. This completes the replication of our paper.

@@

Right before our final submission, we did a final test run on all the programs. We saved all the log files of this particular run in \code{.pdf} format. The correspondence between the log files and the source code is as follows. Once again, to \textit{exactly} replicate what is in these files, the reader needs to use the exact same version of the softwares as we do. The original log files are saved in text files of \code{.log} extension with the same names. For instance, executing the source code \bcode{cpsc\_raw.do} will generate a text log file \bcode{cpsc\_raw.log}, which we converted to \bcode{cpsc\_raw\_log.pdf} manually.
\begin{itemize}
    \item
    \bcode{cpsc\_raw.do} $\longleftrightarrow$ \bcode{cpsc\_raw\_log.pdf}
    \item
    \bcode{cec\_clean.do} $\longleftrightarrow$ \bcode{cec\_clean\_log.pdf}
    \item
    \bcode{cpsc\_convert.R} $\longleftrightarrow$ \bcode{cpsc\_convert\_log.pdf}
    \item
    \bcode{cec\_convert.R} $\longleftrightarrow$ \bcode{cec\_convert\_log.pdf}
    \item
    \bcode{Empirical\_AEJ.R} $\longleftrightarrow$ \bcode{empirical\_main\_log.pdf}
    \item
    \bcode{Empirical\_Appendix.R} $\longleftrightarrow$ \bcode{empirical\_appendix\_log.pdf}
    \item
    \bcode{Descriptive.R} $\longleftrightarrow$ \bcode{descriptive\_log.pdf}
    \item
    \bcode{Accounting.R} $\longleftrightarrow$ \bcode{accounting\_log.pdf}
\end{itemize}
The log files for the quantitative exercises are not automatically generated. We manually copied and pasted the intermediate results sent to the terminal to two text files: \bcode{quantitative\_main.log} for the perfect substitute case in the main text and \bcode{quantitative\_ces.log} for the constant elasticity of substitution case in the appendix. Then we convert the two files to \code{.pdf} format.
\begin{itemize}
    \item
    \bcode{quantitative\_main\_log.pdf} $\longleftrightarrow$ \bcode{quantitative\_main.log}
    \item
    \bcode{quantitaitve\_ces\_log.pdf} $\longleftrightarrow$ \bcode{quantitative\_ces.log}
\end{itemize}
